\huge Tor's Usability for Censorship Circumvention

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Edits.

\item {\bfseries Eliminated technical questions.}  We removed questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer. There are two fewer screens in the interface.
\item {\bfseries Added auto-detect for proxies.} Auto-detection of proxies can be done locally, by scanning system files. This is safe even for at-risk users, and greatly simplifies the configuration process.

\item {\bfseries Switched ordering to configure proxies first.} To build users' mental models, network components are configured in a topologically sequential order. Previously, proxies were put after bridge configuration because only a small fraction of users require proxies. With auto-detection, configuring a proxy before a bridge will not burden the users. 
\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint based progress bar that shows network components involved in connecting to the Tor network. This aligns with the mental model we are trying to build. As connections are made with components, the progress bar displays a green check, giving immediate feedback to the user. For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network. Upon failure, users can see which components have succeeded and which have failed.
\end{enumerate}

The redesigned interface conservatively interacts with users by automating only safe configuration processes and still allowing users to have control over configuring all interacting network components. The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may change as the censorship environments change.

>>>>

\item {\bfseries Eliminated technical questions.}  We removed the gating questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer. There are two fewer screens in the revised interface.
\item {\bfseries Added auto-detection of proxies.} In principle, the interface can guess whether a proxy is needed by scanning the operating system configuration. This purely local detection does not carry the potential risks of network probing and should be safe even for at-risk users. (In our experiment, we simulated the auto-detection by hard-coding the fact that a proxy was not required.)

\item {\bfseries Switched ordering to configure proxies first.} To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen. Previously, proxies were put after bridge configuration because only a small fraction of users require proxies. With auto-detection, configuring a proxy before a bridge burden users less than before.
\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network. This aligns with the mental model we are trying to build. As connections are made with each component, the progress bar displays a green check, giving immediate feedback to the user. For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network. Upon failure, users can see which components have succeeded and which have failed.
\end{enumerate}

The redesigned interface conservatively interacts with users by automating only those configuration processes that are safe to automate, while still allowing users to have control. The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may change as censorship environments change.
